---
title: "asset alloc"
author: "zwl"
date: "27 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r load, echo=FALSE}
fred <- read.csv('~/data/fred_md_preproc.csv')
fred$X <- as.Date(fred$X, format='%m/%d/%Y')

# take out s&p columns
fred2 <- fred %>% select(-c(S.P.500, S.P..indust, S.P.div.yield, S.P.PE.ratio))

# find out how many NAs per example
flag <- is.na(fred2)
na.count <- apply(flag, 1, sum)
plot(x=fred2$X, y=na.count)
```

```{r na.cols}
# find rows with less than 6 na columns
row.flag <- na.count < 6
fred2 <- fred2[row.flag,]
dim(fred2)

# find which columns have NA
col.flag <- is.na(fred2)
na.cols <- apply(col.flag, 2, sum)
# 5 columns have NA values
fred3 <- fred2[, na.cols > 0]
str(fred3)
```

These columns with NA are:

* ACOGNO, New orders for consumer goods, starts 1992/3
* ANDENOx, New orders for durable goods, 1968/3
* TWEXMMTH, Trade weighted USD index, 1973/2
* UMCSENTx, Consumer Sentiment Index, 1978/2
* VXO CBOE S&P 100, starts 1962/7

For each column, find out when the data series started. 

```{r na}
na.df <- cbind(X=fred2$X, fred3)
# convert to long format
na.long <- gather(na.df, field, value, ACOGNO:VXOCLSx)

na.long %>% 
  # Convert variable to factor, so we can use complete later. We do this within
  # group_by, because we want to operate by level of variable
  group_by(field=factor(field)) %>% 
  # Remove all rows of variable if there aren't any rows with values==0
  # filter(any(value==0)) %>% 
  # Remove all rows with values != 0
  # filter(value != 0) %>% 
  filter(!is.na(value)) %>%
  # Keep the first row of each variable, after sorting by Date
  # This gives us the first non-zero row
  arrange(X) %>% 
  slice(1) %>% 
  # Use complete to bring back a row for any level of variable that
  # didn't start with any rows with values==0
  ungroup() %>% 
  complete(field)
```

If we remove New Orders for Consumer Goods, we can go back to 1978/2. 
Or, we try to go to 1962 by removing others. 

```{r final.prep}
fred4 <- fred2 %>% select(-c(ACOGNO, ANDENOx, TWEXMMTH, UMCSENTx))
fred5 <- fred4 %>% na.omit
head(fred5$X)
sum(is.na(fred5))
```

Now we can use this for other analysis.